\documentclass[12pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tcolorbox}

\pagestyle{fancy}
\fancyhf{}
\lhead{Codeferno}
\rhead{Perseverantia 2025}
\cfoot{\thepage}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

\tcbset{
  mybox/.style={
    colback=gray!5,
    colframe=black,
    boxrule=0.4pt,
    sharp corners,
    left=6pt,
    right=6pt,
    top=6pt,
    bottom=6pt
  }
}

\begin{document}

\ifdefined\BOOKLET
  \pagestyle{empty}
\fi

\begin{center}
    {\LARGE \textbf{Welcome to Codeferno}} \\[0.5em]
    \rule{\textwidth}{0.4pt}
\end{center}

\vspace{1em}

\section*{General Information}
\begin{itemize}[leftmargin=1.5em]
    \item Contest Website: \href{http://192.168.68.100:8888}{\texttt{192.168.68.100:8888}}
\item Duration: \textbf{30 minutes (planning) + 90 minutes (coding) = 120 minutes}
\end{itemize}

\section*{Rules \& Guidelines}
\begin{enumerate}[leftmargin=1.5em]
    \item You may use \textbf{C / C++ / Java / Python}.
    \item For Java: 
    \begin{itemize}
        \item The filename must be the \textbf{problem ID}. Example: \texttt{A.java}.
        \item Always include \texttt{public static void main(String[] args)}.
    \end{itemize}
    \item Do \emph{not} print prompts such as \texttt{"Enter n:"}.
    \item Follow the input/output format in the problem statement \textbf{exactly}.  
    Any deviation will cause your submission to fail.  
    \begin{tcolorbox}[mybox]
    For example: If the problem specifies output as  
    \begin{verbatim}
    1 2 3 4 5
    \end{verbatim}  
    and you print  
    \begin{verbatim}
    1
    2
    3
    4
    5
    \end{verbatim}  
    your answer will be marked wrong.
    \end{tcolorbox}
    \item The exact required format will always be clearly specified in each problem.
\end{enumerate}

\section*{Scoring}
\begin{itemize}[leftmargin=1.5em]
    \item Each problem carries a certain number of points.  
    \item Partial scoring will be given for passing some subtasks.  
    \item Ties are broken by \textbf{time of last correct submission}.  
\end{itemize}

\section*{Allowed References}
\begin{itemize}[leftmargin=1.5em]
    \item Documentation provided locally during the contest:  
    \begin{itemize}
        \item Python
        \item C
        \item C++
        \item Java
    \end{itemize}
    \item You may freely refer to the official docs for these languages during the contest. Links are provided in the \texttt{codeferno} folder. 
\end{itemize}

\section*{Prohibited Actions}
\begin{itemize}[leftmargin=1.5em]
    \item No internet access is allowed.  
    \item Do \textbf{not} attempt to Google or consult any other online source.  
    \item Do \textbf{not} attempt to use AI language models or external tools to solve the problems.  
    \item Any violation will result in disqualification.  
\end{itemize}

\vfill
\begin{center}
    \rule{0.8\textwidth}{0.4pt} \\[0.5em]
    \textit{Good luck; may the best coder win!}
\end{center}

\end{document}
